Modalities for Location Virtualization

### 2022-09-20 soundness.tex
+

Together, Theorems~\ref{th:adequacy} and~\ref{th:validity} guarantee that, if
the Hoare triple $\textsf{valid\_init}\instrs\iTrue$ can be obtained by applying
the reasoning rules of our logic, then the program~$\instrs$ is safe.

@@

Since our semantics operates right on top of the x86-64 machine state (with Iris terminology, physical store),
we do not need to augment the physical store for more abstract reasoning, consequently, we do not need to come up
with a complicated logical relations that ties the physical store to the
\logical store. 
\begin{definition}[Relation between Physical and \Logical Stores]
\label{def:related}
  Two stores $\store$ and $\logicalstore$ are \emph{related},
  which we write $\related\store\logicalstore$, when
  they have the same domain.
\end{definition}

>>>>

Together, Theorems~\ref{th:adequacy} and~\ref{th:validity} guarantee that, if
the Hoare triple $\textsf{valid\_init }\instrs\;\iTrue$ can be obtained by applying
the reasoning rules of our logic, then the program~$\instrs$ is safe.

@@

Since our semantics operates right on top of the x86-64 machine state (with Iris terminology, physical store),
we do not need to augment the physical store for more abstract reasoning, consequently, we do not need to come up
with a complicated logical relations that ties the physical store to the
\logical store. 
\begin{definition}[Relation between Physical and \Logical Stores]
  \label{def:related}
  Since we pick the logical store exactly same with physical store,  
  two stores are \emph{related}, identical.
\end{definition}
